Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-25 manuscript/manuscript.tex
section 3

\paragraph{\textbf{Step 1}: Conditional MSN Imputation} The sampler begins with imputing missing values $\mathbf{y}_i^{miss}$ conditional on current simulated values of $z_i = k$ and $t_i$ as well as the associated $\mathbf{y}_i^{obs}$. This is accomplished by drawing $\mathbf{y}_i^{miss}$ from $\text{N}_{J-q_i}(\boldsymbol\mu^{cond}_{ki},\boldsymbol\Sigma^{cond}_k)$ as described in \ref{eq:impute}.

>>>>

\paragraph{\textbf{Step 1}: Conditional MSN Imputation} The sampler begins with imputing missing values $\mathbf{y}_i^{miss}$ conditional on current simulated values of $z_i = k$ and $t_i$ as well as the associated $\mathbf{y}_i^{obs}$. This is accomplished by drawing $\mathbf{y}_i^{miss}$ from $\text{N}_{J-q_i}(\boldsymbol\mu^{cond}_{ki},\boldsymbol\Sigma^{cond}_k)$ as described in equation \ref{eq:impute} for all $i = 1,...,n$. Conditional imputation is completed with construction of a complete outcome vector $\mathbf{y}_i$ by merging the now imputed $\mathbf{y}_i^{miss}$ with $\mathbf{y}_i^{obs}$ with respect for the original order of $\mathbf{y}_i$.

\paragraph{\textbf{Step 2:} Update of MSN Regression Parameters}
